% LaTeX resume using res.cls
\documentclass{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font  
\usepackage{comment}
\setlength{\topmargin}{-0.6in}  % Start text higher on the page 
\setlength{\textheight}{9.8in}  % increase textheight to fit more on a page
\setlength{\evensidemargin}{-0.5in}
\setlength{\oddsidemargin}{-0.5in}
\setlength{\textwidth}{6.3in}
\setlength{\headsep}{0.15in}     % space between header and text
\setlength{\headheight}{12pt}   % make room for header
\usepackage{fancyhdr}  % use fancyhdr package to get 2-line header
\renewcommand{\headrulewidth}{0pt} % suppress line drawn by default by fancyhdr
\lhead{\hspace*{-\sectionwidth}Miguel Pinilla} % force lhead all the way left
\rhead{Page \thepage}  % put page number at right
\cfoot{}  % the footer is empty
\pagestyle{fancy} % set pagestyle for the document


\begin{document}



\thispagestyle{empty} % this page does not have a header


\name{MIGUEL PINILLA}
\address{51 Roslyn Avenue\https://www.overleaf.com/project/50f8ddca24a73f303b1575c2\San Carlos, Ca, 94070}
\address{+1.650.489.0329\\jmpicnic@gmail.com\\www.linkedin.com/in/mpinilla}

\begin{resume}

\section{SUMMARY}

\begin{itemize}
\item Over 20 year of successful technology and engineering leadership, with more than 10 as an executive responsible for product and technology strategy.
\item A passion and proven record building teams and delivering products and innovation to customers.
\item Managed complex product portfolios and roadmaps for very large organizations with complex offerings to the market.
\item A deep technical expertise in Software, Operations and Processes allows me to lead high performance teams and scale organizations from small start up teams to large multi-national groups.
\item Hands on experience on a variety of Product Development methodologies, having lead agile practices in small companies and agile transformations in multi-national public companies.
\end{itemize}


\section{EXPERIENCE}
{\bf Since 2/2019 CTO, Crux Systems, Track \& Trace Engineering at Flexport.} Responsible for the technology and platform of Crux Systems, a start-up providing end-to-end visibilty and collaboration to the back-bone supply chain (www.cruxsystems.com). Over the first 7 months of 2019, cargo tracked on the platform grew five fold, successfully scaling the platform and technology. Crux had a successful exit when it was acquired by Flexport in November 2019.

{\bf Since 1/2019 Principal, Salduba Technologies} Founded a Supply Chain strategy consulting practice: www.saldubatech.com

\begin{bf}
VP, Product \& Technology Strategy, KION Group. 01/2017-12/2018
\end{bf}

After the acquisition of Dematic by KION Group in November 2016, and reporting to KION Group's CTO, I took over the responsible to formulate and establish the KION's global product strategy and unify its technology and innovation initiatives, leading a team of 150 professionals in 15 locations across the globe. KION Group is a public company with operations globaly through 5 separate operating units and a product portfolio of 6 brands with more than 600 product models.

\begin{bf}
VP, Global Logistics Solutions, Dematic Corp. 03/2014-12/2016
(Acquired by KION Group)
\end{bf}

Responsible for global product strategy and management, as well as research and innovation in advanced software architectures. Starting in FY16 (10/2015) I became responsible for product commercialization and R\&D process excellence initiatives. Starting in FY17 (10/2016), we formed a new Operations Research Development and Innovation team under my leadership.

{\bf Principal, Platform Development, Elementum (Flextronics, Supply Chain Software Industry). 06/2013-03/2014}

Responsible for the development of Elementum's technology platform (www.elementum.com), a Multi-Tenant, Multi-enterprise Supply Chain Execution System that offers large enterprises visibility and transactional collaboration around supply chain transactions.


{\bf VP, Engineering. VP, Architecture, Sunrun (www.sunrun.com). 03/2011-03/2013}

Responsible for all technology initiatives supporting the company business and its network of suppliers, partners and customers during a period of rapid growth. During this period, my team overhauled Sunrun's IT infrastructure introducing Oracle ERP and an enterprise data warehouse. Rebuilt the energy production monitoring and billing systems and developed and launched a new sales and design tool using satelite maps and images of residential roofs with evaluation solar access and support for solar system design.


{\bf VP Product Development, On Demand Products. Redprairie corporation (now part of JDA), 05/2010-03/2011}

Responsible for all product development and delivery (Product Management, Engineering, Technical Operations) for the SaaS products for Redprairie. This was a result of the acquisition of SmartTurn by Redprairie.


{\bf CTO and VP, Engineering. SmartTurn (www.smartturn.com),12/2007-04/2010}
    
Responsible for all product development and delivery at SmartTurn, a pioneer, leading provider of SaaS Supply Chain and Warehouse Management Software. Developed from scratch the product and SaaS platform and, with the CEO built the company from the spinoff out of Navis, through its launch and growth and sale to RedPrairie

After successfully launching the product and grown the customer base, the company was sold to Redprairie corp, which is now part of JDA. Currently the SmartTurn product is run and operated by DiCentral.

{\bf Senior Director, Development. Navis LLC (now part of Cargotec), 07/2003-12/2007}

Responsible for new generation marine systems (Container Terminal Management) including a SaaS system to manage container depots and initiating the company business intelligence product. Led a team of engineers in California and Oakland

{\bf VP, Engineering. Recipio/Informative (now part of Satmetrix, Market Research Industry), 04/2000-07/2003}

    Responsible for all product development of the “Voice of the Customer” solution, based on a patent shared with the founder and the CTO of the company. 


{\bf Software Development Manager. Alcatel (Now lucent), Broadband Division, 06/1988-09/1996}

Responsible for a multi-team development group that developed the Operation and Maintenance software for the A-1000 ATM broadband switches.

\section{EDUCATION AND OTHER}

%vspace{0.1in}
    
\begin{itemize}
    \item {\bf PhD, Stanford University, 2001}
    \begin{itemize}
        \item Manufacturing Information Systems (within Mech Eng Department)
        \item SAP Fellow, Future Professors of Manufacturing Program. Stanford University
    \end{itemize}
    \item {\bf INSEAD Business School} Executive Education, 2018
    \item {\bf IESE Business School} Executive Education, (Madrid/Barcelona), 1996
    \item {\bf Carnegie Mellon University}, Master of Engineering. Computer Aided Manufacturing (Mechanical Engineering), 1987
    \item {\bf Fulbright Scholar}, 1986
    \item {\bf Pontificial University of Comillas in Madrid, Spain.} Senior Engineer (MSc equivalent). Industrial Engineering. Graduated with “Extraordinary University Award”, 1985
    \item Multiple collaborations with Stanford and Comillas University as academic advisor and consultant.
    \item Multiple patents and technical papers in peer reviewed conferences and journals.
\end{itemize}

\end{resume}
\end{document}


