% LaTeX resume using res.cls
\documentclass{res}
\usepackage{hyperref}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font  
\usepackage{comment}
\setlength{\topmargin}{-0.6in}  % Start text higher on the page 
\setlength{\textheight}{9.8in}  % increase textheight to fit more on a page
\setlength{\evensidemargin}{-0.5in}
\setlength{\oddsidemargin}{-0.5in}
\setlength{\textwidth}{6.3in}
\setlength{\headsep}{0.15in}     % space between header and text
\setlength{\headheight}{12pt}   % make room for header
\usepackage{fancyhdr}  % use fancyhdr package to get 2-line header
\renewcommand{\headrulewidth}{0pt} % suppress line drawn by default by fancyhdr
\lhead{\hspace*{-\sectionwidth}Miguel Pinilla} % force lhead all the way left
\rhead{Page \thepage}  % put page number at right
\cfoot{}  % the footer is empty
\pagestyle{fancy} % set pagestyle for the document

\begin{document}

\thispagestyle{empty} % this page does not have a header

\name{
\centering
Miguel Pinilla
}

\begin{resume}

\begin{table}[h]
\centering
\begin{tabular}{c}
51 Roslyn Avenue, San Carlos, Ca, 94070\\
+1.650.489.0329, \href{mailto://jmp@alumni.stanford.edu}{jmp@alumni.stanford.edu}\\
\href{https://www.linkedin.com/in/mpinilla/}{\it www.linkedin.com/in/mpinilla/}
\end{tabular}
\end{table}
\vspace{0.1in}

    During my career, I have successfully defined and executed product and technology strategies for both startups and multi-national groups and led teams implementing them. I am passionate about bringing innovation to solve customer challenges in logistics and supply chains. With well-recognized expertise in the logistics industry and technology, I have served in executive and C-level roles, shaping company innovation strategies, building, and mentoring high-performance organizations. My dual citizenship in Europe and the US enables me to work across cultural and geographic boundaries.

\begin{comment}
\begin{itemize}
\item 
\item My passion for solving the supply chain challenges of large Deep technical expertise that allows me to lead highly capable teams.
\item A passion to develop the engineering teams that build and deliver software products.
\item Hands on experience on a variety of Software Development methodologies, with multiple years of agile practice with Scrum based teams.
\end{itemize}
\end{comment}

\section{EXPERIENCE}
{\bf 10/2023- Author and Consulting} Authored the book \href{https://amzn.to/4d4CFqn}{\em The Warehouse Revolution}, published by \href{https://www.businessexpertpress.com/}{\em Business Expert Press} with multiple weeks in best selling new release in its category at Amazon. Principal of \href{https://www.salduba.info/}{Salduba Technologies}, advising start-ups and investors in the supply chain industry.

{\bf 2017- Mentor, Swartz Center for Entrepreneurship. Carnegie Mellon University} \href{https://www.cmu.edu/swartz-center-for-entrepreneurship/get-involved/mentor/mentors-bio-pages/pinilla.html}{\it https://www.cmu.edu/swartz-center-for-entrepreneurship/get-involved/mentor/index.html} Mentor and advise early-stage entrepreneurs, judge of \href{https://www.cmu.edu/swartz-center-for-entrepreneurship/events/mcginnis-venture-competition/index.html}{McGinnis Venture Competition}

{\bf 10/2019-10/2023, Senior Technical Fellow, Flexport} {\it www.flexport.com} Responsible for the definition and technology of the new Flexport Operating System Platform. Senior member of the technical team.

{\bf 2/2019 until acquisition by Flexport (11/2019), CTO, Crux Systems} {\it www.cruxsystems.com} Responsible for all the product and technology development at Crux, including algorithms for search and reconciliation of shipment tracking information across multiple data sources.

{\bf 12/2016-12/2018 VP, Product and Technology Strategy, KION Group} {\it www.kiongroup.com}
After KION Group acquired Dematic, I took the responsibility to lead product strategy, technology innovation, and IP portfolio for all five business units, over 600 products, and R\&D programs including fuel cell technology, robotics, autonomous vehicles, cloud systems, and IoT. KION's R\&D centers spanned the United States, Australia, China, India, Eastern Europe, and the EU, collaborating with research institutes (e.g. \href{https://www.fraunhofer.de/en.html}{Fraunhofer Institute} , universities (e.g. \href{https://msande.stanford.edu/}{Stanford Management Science \& Engineering}, and other technology partners.

{\bf  03/2014, 12/2016 VP, Global Logistics Solutions, Dematic} {\it www.dematic.com}. I was responsible for all product strategy and management as part of the company's R\&D function. Rebuilt the product management organization and introduced disciplined product portfolio management in the company. Rationalized the product lines and established an agile product development process with three development cycles per year, where it had been multi-year project cycles. Dematic was sold to KION Group for over \$3Bn on the strength of its market position and its product portfolio.

{\bf  06/2013-03/2014 Principal, Platform Development, Elementum (Flextronics)}\newline
{\it www.elementum.com} Responsible for the development of Elementum's technology platform, a Multi-Tenant, Multi-enterprise Supply Chain Execution System that offers large enterprises visibility and transactional collaboration.

%\vspace{0.1in}
%\subsection{03/2011-Present: Renewable Energy}
{\bf 03/2011-06/2013 VP, Engineering. VP, Architecture, Sunrun}
{\it www.sunrun.com} Responsible for all technology initiatives to support the company business and its network of suppliers, partners, and customers during a period of rapid growth. During this time, I reconstituted and grew the engineering team six fold in 6 months, introduced enterprise level systems (Oracle ERP, Data Warehouse) and lead the overhaul for scalability of the company's distributed power generation infrastructure 

\begin{comment}
\begin{itemize}
    \item Reconstituted the engineering team, growing it from 10 to ~60 engineers in the first 9 months.
    \item Upgraded the financial infrastructure of the company from Quickbooks to Oracle EBS R12.
    \item Delivered a Data analytics platform for the company that integrates all sources of data in an enterprise Data Warehouse.
    \item Stabilized existing systems (Lead-to-Quote systems, Billing, Monitoring) that allowed the company to double its customer base in 12 months.
    \item Developed from scratch an industry leading Solar PV System Design Tool.
    \item Delivered new, scalable Customer and Corporate websites integrated with the company back office systems.
    \item Re-architected the core systems of the company to scale to up to 10x the number of customers to support the growth targets of the company (under current implementation).
    \item Developed a financial modeling package in Python for direct use by financial analyst that reduces analysis time by a factor of 10-50 w.r.t. Excel.
\end{itemize}
\end{comment}

%\subsection{07/2003-03/2011: Supply Chain Software Systems}
{\bf 05/2010-03/2011 VP Product Development, On Demand Products. Redprairie corporation (now part of JDA)}
{\it blueyonder.com/solutions/warehouse-management}
Responsible for all product development and delivery (Product Management, Engineering, Technical Operations) for the SaaS products for Redprairie.
\begin{comment}
\begin{itemize}
    \item Led, with the General Manager of the On-Demand Division, the integration of SmartTurn into Redprairie.
    \item Developed industry leading pick and ship algorithms for high volume warehouses.
\end{itemize}
\end{comment}
%\newpage

{\bf 12/2007 until acquisition by RedPrairie in 04/2010 CTO. SmartTurn}
{\it www.smartturn.com}
Responsible for all product development and delivery at SmartTurn, a pioneer, leading provider of SaaS Supply Chain and Warehouse Management Software. I, together with the CEO, spun off SmartTurn out of Navis LLC and secured venture financing from NEA and Emergence Capital. After growing the company and the business, SmartTurn was acquired by Redprairie Corp in 2010.
\begin{comment}
\begin{itemize}
    \item Spun off SmartTurn out of Navis LLC with the CEO and secured VC financing from NEA and Emergence Capital.
    \item Delivered the pioneer Saas WMS system, including mobile application,  securing over 100 customers in industries from Banking to Logistics and Retail.
    \item Created and managed the technology team.
    \item Managed (with the CEO) the sale of the company to Redprairie Corp.
\end{itemize}
\end{comment}

{\bf 07/2003-12/2007 Senior Director, Development. Navis LLC (now part of Cargotec)}
{\it www.navis.com}  Delivered an early Saas system to manage Container Depots and, together with the CTO, was responsible for the new generation marine systems terminal operating system.
\begin{comment}
\begin{itemize}
    \item Responsible for new generation marine systems (Container Terminal Management)
    \item Delivered an early Saas system to manage Container Depots.
    \item Initiated a Business Intelligence Solution integrated with the core terminal management software.
    \item Lead a development group with multiple teams, distributed between California and Chennai (India).
    \item Defined the “Go To Market” process that was adopted by the engineering organization as the standard development process.
\end{itemize}
\end{comment}

%\subsection{04/2000-07/2003 CRM/Market Research Software}
{\bf VP, Engineering. Recipio/Informative (now part of Satmetrix)}
{\it www.satmetrix.com/software/}
Responsible for all product development of the {\em Voice of the Customer}, based on a patent shared with the founder and the CTO of the company. 
\begin{comment}
\begin{itemize}
    \item Delivered the solution (Saas) to large customer oriented enterprises, including NBC, Procter and Gamble, General Motors and Lego.
    \item Managed the integration of the technical teams through the acquisition of Recipio by Informative.
\end{itemize}
\end{comment}
%\subsection{06/1988-09/1996 Telecommunications}

{\bf Software Development Manager. Alcatel (now lucent), Broadband Division}
{\it www.alcatel-lucent.com}
Responsible for a multi-team development group that developed the Operation and Maintenance software for the A-1000 ATM broadband switches.
\begin{comment}
\begin{itemize}
    \item Delivered the Operation and Maintenance Software for the first generation of A-1000 ATM switches
    \item Member of the corporate systems architecture for the A-1000 ATM broadband switches.
\end{itemize}
\end{comment}

\section{Education}

\vspace{0.2in}
\begin{itemize}
    \item PhD, Manufacturing Information Systems (within Mech Eng Department), Stanford University
    \item SAP Fellow, Future Professors of Manufacturing Program. Stanford University
    \item Executive Education, INSEAD business school (Fontainebleau)
    \item Executive Education, IESE business school (Madrid/Barcelona)
    \item M.Eng. Computer Aided Manufacturing (Mech Eng). Carnegie Mellon University.
    \item Fulbright Scholar
    \item Senior Engineer (MSc equivalent). Industrial Engineering. Pontificial University of Comillas in Madrid, Spain. Graduated with “Extraordinary University Award”
    \item Multiple collaborations with Stanford and Comillas University as advisor or consultant.
    \item Multiple patents and technical papers in peer reviewed conferences and journals.
    \item Dual citizenship US/Europe(Spain).
\end{itemize}

\section{Other}

Please see online:

\begin{itemize}
\item Publications List in LinkedIn: \href{https://www.linkedin.com/in/mpinilla/details/publications/}{\em https://www.linkedin.com/in/mpinilla/details/publications/}
\item Publications in Academia.edu: \href{https://stanford.academia.edu/MPinilla}{\em https://stanford.academia.edu/MPinilla}
\item Patent list in LinkedIn: \href{https://www.linkedin.com/in/mpinilla/details/patents/}{\em https://www.linkedin.com/in/mpinilla/details/patents/}
\item Medium Publication: \href{https://medium.com/salduba}{\em https://medium.com/salduba}
\begin{itemize}
\item LinkedIn Version: \href{https://www.linkedin.com/newsletters/7168774727367409664/}{\em https://www.linkedin.com/newsletters/7168774727367409664/}
\end{itemize}
\end{itemize}

\end{resume}
\end{document}