% LaTeX resume using res.cls
\documentclass{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font  
\usepackage{comment}
\setlength{\topmargin}{-0.6in}  % Start text higher on the page 
\setlength{\textheight}{9.8in}  % increase textheight to fit more on a page
\setlength{\evensidemargin}{-0.5in}
\setlength{\oddsidemargin}{-0.5in}
\setlength{\textwidth}{6.3in}
\setlength{\headsep}{0.15in}     % space between header and text
\setlength{\headheight}{12pt}   % make room for header
\usepackage{fancyhdr}  % use fancyhdr package to get 2-line header
\renewcommand{\headrulewidth}{0pt} % suppress line drawn by default by fancyhdr
\lhead{\hspace*{-\sectionwidth}Miguel Pinilla} % force lhead all the way left
\rhead{Page \thepage}  % put page number at right
\cfoot{}  % the footer is empty
\pagestyle{fancy} % set pagestyle for the document


\begin{document}



\thispagestyle{empty} % this page does not have a header


\name{MIGUEL PINILLA}
\address{51 Roslyn Avenue\\San Carlos, Ca, 94070}
\address{+1.650.489.0329\\jmpicnic@gmail.com\\www.linkedin.com/in/mpinilla}

\begin{resume}

\section{SUMMARY}

\begin{itemize}
\item Over 20 year of technology and engineering leadership, with more than 10 in executive positions with a passion to build teams delivering products and new technologies to customers and the market.
\item Proven delivery of business value to customers through successful enterprise products.
\item Managed complex product portfolios and roadmaps for very large organizations with complex offerings to the market.
\item Deep technical expertise in Software, Operations and Processes that allows me to lead high performance technical teams and scale organizations from small start up teams to large corporate groups.
\item Hands on experience on a variety of Software Development methodologies, with multiple years of agile practice with Scrum based teams.
\end{itemize}


\section{EXPERIENCE}

\begin{bf}
VP, Product \& Technology Strategy, KION Group. 01/2017-Current
\end{bf}

After the acquisition of Dematic by KION Group in November 2016, and reporting to KION Group's CTO, I took over the responsible to formulate and establish the group's global product strategy and unify its technology and innovation initiatives with a team of 150 professionals in 15 locations across the globe. KION Group is a public company with operations globaly through 5 separate operating units and a product portfolio of 6 brands with more than 600 product models.
\begin{itemize}
    \item Structured the product roadmap and portfolio process at the group level, coordinating the product definition across the 5 P\&L operating units of the group and the technical product development tools, increasing the visibility and rigor of R\&D investment decisions and priorities in KION.
    \item Lead the technology and Innovation activities of the group with projects ranging from Fuel Cell development, to Robotics, IoT, Operations Optimization and software cloud systems. These programs included collaboration with key universities and institutions in Europe and North America, as well as partnerships with other industrial and technology companies.
    \item Introduced Agile methodologies and processes in the CTO organization, including mechatronics development, controls, software and autonomous vehicles.
\end{itemize}

\begin{bf}
VP, Global Logistics Solutions, Dematic Corp. 03/2014-12/2016
(Acquired by KION Group)
\end{bf}

Responsible for global product strategy and management, as well as research and innovation in advanced software architectures. Starting in FY16 (10/2015) I also became responsible for product commercialization and R\&D process excellence initiatives. Starting in FY17 (10/2016), we formed a new Operations Research Development and Innovation team under my leadership.

\begin{itemize}
    \item Established the Product Management Function and processes with Global Scope. Growing the team from ~20 to 40 product and program managers globally.
    \item Defined and lead the creation of a Strategic product road-map as part of the Annual company strategic plan, which resulted in better use of R\&D resources and the coordination of the multiple development teams in the company (Software, Controls,  Mechatronics)
    \item Introduced (including change management) industry leading agile development processes to R\&D that have resulted in significant reductions of time to market of products, improved executive management visibility and improved application of R\&D resources.
    \item Established market driven pricing policies for products and customer quotes (as opposed to Cost-Plus quoting) resulting in better margin protection for Dematic Products and increased visibility at a global level of product performance.
    \item Rationalized the product offering of Dematic by introducing a global product catalog, a product and program portfolio management and the associated tracking and metrics.
    \item Together with the Global R\&D EVP and the Global CEO, developed an strategic vision for the supply chain industry to lead our investment strategy and position the company as a technology leader in the sector.
\end{itemize}

{\bf Principal, Platform Development, Elementum (Flextronics, Supply Chain Software Industry). 06/2013-03/2014}

Responsible for the development of Elementum's technology platform, a Multi-Tenant, Multi-enterprise Supply Chain Execution System that offers large enterprises visibility and transactional collaboration around supply chain transactions.
\begin{itemize}
    \item Built the technology team hiring ~20 engineers in a period of 6 months
    \item Defined the core capabilities of the platform and delivered the first alpha versions of the software with the new team.
\end{itemize}

{\bf VP, Engineering. VP, Architecture, Sunrun. 03/2011-03/2013}

Responsible for all technology initiatives to support the company business and its network of suppliers, partners and customers during a period of rapid growth. The technology team during this time:
\begin{itemize}
    \item Reconstituted the engineering team, growing it from 10 to ~60 engineers in the first 9 months.
    \item Upgraded the financial and backbone business processes infrastructure of the company from Quickbooks to Oracle EBS R12 and created an analytics platform for the company that integrates all sources of data in an enterprise Data Warehouse.
    \item Stabilized existing systems (Lead-to-Quote systems, Billing, Monitoring) that were under severe scaling pressure to allow doubling the  customer base in 12 months.
    \item Developed from scratch an industry leading Solar PV System Design Tool.
    \item Delivered new, scalable Customer and Corporate websites integrated with the company back office systems.
    \item Re-architected the core monitoring and billing systems of the company to scale to up to 10x the number of customers to support the growth targets of the company (under development at the end of my tenure).
    \item Developed a financial modeling toolset to develop sophisticated financial instruments for Residential Solar financing.
\end{itemize}


{\bf VP Product Development, On Demand Products. Redprairie corporation (now part of JDA), 05/2010-03/2011}

Responsible for all product development and delivery (Product Management, Engineering, Technical Operations) for the SaaS products for Redprairie. This was a result of the acquisition of SmartTurn by Redprairie.
\begin{itemize}
    \item Led, with the General Manager of the On-Demand Division, the integration of SmartTurn into Redprairie.
    \item Developed industry leading pick and ship algorithms for high volume warehouses.
\end{itemize}

{\bf CTO and VP, Engineering. SmartTurn,12/2007-04/2010}
    
Responsible for all product development and delivery at SmartTurn, a pioneer, leading provider of SaaS Supply Chain and Warehouse Management Software.
\begin{itemize}
    \item Spun off SmartTurn out of Navis LLC with the CEO and secured VC financing from NEA and Emergence Capital.
    \item Delivered the pioneer Saas WMS system, including mobile application,  securing over 100 customers in industries from Banking to Logistics and Retail.
    \item Created and managed the technology team.
    \item Managed (with the CEO) the sale of the company to Redprairie Corp.
\end{itemize}
After successfully launching the product and grown the customer base, the company was sold to Redprairie corp, which is now part of JDA. Currently the SmartTurn product is run and operated by DiCentral.

{\bf Senior Director, Development. Navis LLC (now part of Cargotec), 07/2003-12/2007}

Responsible for new generation marine systems (Container Terminal Management)
\begin{itemize}
    \item Delivered an early Saas system to manage Container Depots.
    \item Initiated a Business Intelligence Solution integrated with the core terminal management software.
    \item Lead a development group with multiple teams, distributed between California and Chennai (India).
    \item Defined the “Go To Market” process that was adopted by the engineering organization as the standard development process.
\end{itemize}

{\bf VP, Engineering. Recipio/Informative (now part of Satmetrix, Market Research Industry), 04/2000-07/2003}

    Responsible for all product development of the “Voice of the Customer” solution, based on a patent shared with the founder and the CTO of the company. 
\begin{itemize}
    \item Delivered the solution (Saas) to large customer oriented enterprises, including NBC, Procter and Gamble, General Motors and Lego.
    \item Managed the integration of the technical teams through the acquisition of Recipio by Informative.
\end{itemize}

{\bf Software Development Manager. Alcatel (Now lucent), Broadband Division, 06/1988-09/1996}

Responsible for a multi-team development group that developed the Operation and Maintenance software for the A-1000 ATM broadband switches.
\begin{itemize}
    \item Delivered the Operation and Maintenance Software for the first generation of A-1000 ATM switches
    \item Member of the corporate systems architecture for the A-1000 ATM broadband switches.
\end{itemize}


\section{EDUCATION AND OTHER}

%vspace{0.1in}
    
\begin{itemize}
    \item {\bf PhD, Stanford University, 2001}
    \begin{itemize}
        \item Manufacturing Information Systems (within Mech Eng Department)
        \item SAP Fellow, Future Professors of Manufacturing Program. Stanford University
    \end{itemize}
    \item {\bf INSEAD Business School} Executive Education, 2018
    \item {\bf IESE Business School} Executive Education, (Madrid/Barcelona), 1996
    \item {\bf Carnegie Mellon University}, Master of Engineering. Computer Aided Manufacturing (Mechanical Engineering), 1987
    \item {\bf Fulbright Scholar}, 1986
    \item {\bf Pontificial University of Comillas in Madrid, Spain.} Senior Engineer (MSc equivalent). Industrial Engineering. Graduated with “Extraordinary University Award”, 1985
    \item Multiple collaborations with Stanford and Comillas University as academic advisor and consultant.
    \item Multiple patents and technical papers in peer reviewed conferences and journals.
\end{itemize}


\end{resume}
\end{document}


